Supporting Information

### 2018-04-05 SupportingInformation.Rmd
minor modification in ext risk plot

### LC model :

  *  As expected, when extinction risk calculated after $25$ years, was plotted against each $d$ (=degree of dispersion) we varied, we found that extinction risk was higher for data came from left tail dependent environmental fluctuations than right tail dependent one. With increasing $numlocs$ from $5$ to $25$, extinction risk decreased [for a fixed $d$] ; [see Figure \ref{fig_risk_r0_numlocs5} - Figure \ref{fig_risk_r0_numlocs25}].

### Ricker model :

 *  For ricker model when extinction risk calculated after $25$ years, was plotted against each $d$ (=degree of dispersion) we varied, we found that extinction risk was higher for data came from left tail dependent environmental fluctuations than right tail dependent one upto $r=0.7$. For $r>0.7$, extinction risk is greater for data came from right tail dependent environmental fluctuations.

  * With increasing $K$ from $50$ to $200$, extinction risk in both case gets decreased as expected. [see Figure \ref{fig_risk_r0.05} - Figure \ref{fig_risk_r0.05_K200}]

 * With increasing $numlocs$ from $5$ to $25$, extinction risk decreased [for a fixed $d$] ; [see Figure \ref{fig_risk_r0.05} and Figure \ref{fig_risk_r0.05_numlocs25}].

@@

# plot for local dispersal in D matrix ; r=0 for LC model, r!=0 for Ricker model
pdf("./Results/ext_risk_local_disp.pdf",heigh=6,width=10)
op<-par(mfrow=c(3,4),mar=c(5,4,1,1) + 0.2)
for(r in rlist){
    cat("r=",r,"\n")
    s<-varying_d(numsims=10000,numsteps =25,numlocs=5,r=r,K=50,disp_everywhere=F,ploton=F)
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend(x=-0.06,y=1.1, c("noise : left","noise : right"), fill=c('red', 'blue'), horiz=T, bty='n')
    mtext(paste0("r = ", r))
}
par(op)
dev.off()

# plot for global dispersal in D matrix ; r=0 for LC model, r!=0 for Ricker model
pdf("./Results/ext_risk_global_disp.pdf",heigh=6,width=10)
op<-par(mfrow=c(3,4),mar=c(5,4,1,1) + 0.2)
for(r in rlist){
  cat("r=",r,"\n")
  s<-varying_d(numsims=10000,numsteps =25,numlocs=5,r=r,K=50,disp_everywhere=T,ploton=F)
  plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d_seq,s$risk_right,type="b",col="blue")
  legend(x=-0.06,y=1.1, c("noise : left","noise : right"), fill=c('red', 'blue'), horiz=T, bty='n')
  mtext(paste0("r = ", r))
}
par(op)
dev.off()

# plot to show the effect of increasing numlocs for r=0 (LC model), r=0.25 (Ricker model)
pdf("./Results/ext_risk_numlocs_effect.pdf",heigh=6,width=6)
op<-par(mfrow=c(2,2),mar=c(4,4,1,1) + 0.1)
for(r in c(0,0.25)){
  cat("r=",r,"\n")
  s5<-varying_d(numsims=10000,numsteps =25,numlocs=5,r=r,K=50,disp_everywhere=T,ploton=F)
  s25<-varying_d(numsims=10000,numsteps =25,numlocs=25,r=r,K=50,disp_everywhere=T,ploton=F)

@@

# Explore equal_dispersal everywhere

### LC model :

    * No effect here.

### Ricker model :

  * With increasing $K$ from $50$ to $200$, extinction risk in both case gets decreased as expected. [see Figure \ref{fig_risk_r0.05_disp_everywhere} - Figure \ref{fig_risk_r0.05_K200_disp_everywhere}]

 * With increasing $numlocs$ from $5$ to $25$, extinction risk decreased [for a fixed $d$] ; [see Figure \ref{fig_risk_r0.05_disp_everywhere} and Figure \ref{fig_risk_r0.05_numlocs25_disp_everywhere}].

>>>>

@@

# plot for local dispersal in D matrix ; r=0 for LC model, r!=0 for Ricker model
pdf("./Results/ext_risk_local_disp.pdf",heigh=6,width=10)
op<-par(mfrow=c(3,4),mar=c(5,4,1,1) + 0.2)
for(r in rlist){
    #cat("r=",r,"\n")
    s<-varying_d(numsims=10000,numsteps =25,numlocs=5,r=r,K=50,disp_everywhere=F,ploton=F)
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend(x=-0.06,y=1.1, c("noise : left","noise : right"), fill=c('red', 'blue'), horiz=T, bty='n')
    mtext(paste0("r = ", r))
}
par(op)
dev.off()

# plot for global dispersal in D matrix ; r=0 for LC model, r!=0 for Ricker model
pdf("./Results/ext_risk_global_disp.pdf",heigh=6,width=10)
op<-par(mfrow=c(3,4),mar=c(5,4,1,1) + 0.2)
for(r in rlist){
  #cat("r=",r,"\n")
  s<-varying_d(numsims=10000,numsteps =25,numlocs=5,r=r,K=50,disp_everywhere=T,ploton=F)
  plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d_seq,s$risk_right,type="b",col="blue")
  legend(x=-0.06,y=1.1, c("noise : left","noise : right"), fill=c('red', 'blue'), horiz=T, bty='n')
  mtext(paste0("r = ", r))
}
par(op)
dev.off()

# plot to show the effect of increasing numlocs for r=0 (LC model), r=0.25 (Ricker model)
pdf("./Results/ext_risk_numlocs_effect_local_disp.pdf",heigh=6,width=6)
op<-par(mfrow=c(2,2),mar=c(4,4,1,1) + 0.1)
for(r in c(0,0.25)){
  #cat("r=",r,"\n")
  s5<-varying_d(numsims=10000,numsteps =25,numlocs=5,r=r,K=50,disp_everywhere=F,ploton=F)
  s25<-varying_d(numsims=10000,numsteps =25,numlocs=25,r=r,K=50,disp_everywhere=F,ploton=F)

# plot to show the effect of increasing numlocs for r=0 (LC model), r=0.25 (Ricker model)
pdf("./Results/ext_risk_numlocs_effect_global_disp.pdf",heigh=6,width=6)
op<-par(mfrow=c(2,2),mar=c(4,4,1,1) + 0.1)
for(r in c(0,0.25)){
  #cat("r=",r,"\n")
  s5<-varying_d(numsims=10000,numsteps =25,numlocs=5,r=r,K=50,disp_everywhere=T,ploton=F)
  s25<-varying_d(numsims=10000,numsteps =25,numlocs=25,r=r,K=50,disp_everywhere=T,ploton=F)

@@

### LC model (r=0) :

  * For LC model, as expected, when extinction risk calculated after $25$ years, was plotted against each $d$ (=degree of dispersion) we varied, we found that extinction risk was higher for data came from left tail dependent environmental fluctuations than right tail dependent one. [see first plot of Figure \ref{fig_risk_local_disp} and Figure \ref{fig_risk_global_disp}]

### Ricker model (r $\neq$ 0):

 *  For ricker model when extinction risk calculated after $25$ years, was plotted against each $d$ (=degree of dispersion) we varied, we found that extinction risk was higher for data came from left tail dependent environmental fluctuations than right tail dependent one upto $r=0.7$. For $r>0.7$, extinction risk is greater for data came from right tail dependent environmental fluctuations. [see Figure \ref{fig_risk_local_disp} - \ref{fig_risk_global_disp}]

  * With increasing $K$ from $50$ to $200$, extinction risk in both case gets decreased as expected. [see Figure \ref{fig_risk_K_effect}]

With increasing $numlocs$ from $5$ to $25$, extinction risk decreased [for a fixed $d$] ; [see Figure \ref{fig_risk_numlocs_effect_local_disp} - Figure \ref{fig_risk_numlocs_effect_global_disp}] for both model.

![Extinction_Risk_local_dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_local_disp}](./Results/ext_risk_local_disp.pdf){ width=40%, height=40% }

![Extinction_Risk_global_dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_global_disp}](./Results/ext_risk_global_disp.pdf){ width=40%, height=40% }

![Extinction_Risk_numlocs_effect_local_disp; numsteps=25, numsims=10000\label{fig_risk_numlocs_effect_local_disp}](./Results/ext_risk_numlocs_effect_local_disp.pdf){ width=40%, height=40% }

![Extinction_Risk_numlocs_effect_global_disp; numsteps=25, numsims=10000\label{fig_risk_numlocs_effect_global_disp}](./Results/ext_risk_numlocs_effect_global_disp.pdf){ width=40%, height=40% }

![Extinction_Risk_K_effect on Ricker model; r=0.25, numsteps=25, numsims=10000\label{fig_risk_K_effect}](./Results/ext_risk_K_effect.pdf){ width=40%, height=40% }
